### 2018-06-30 README.Rmd
tidy up docs

```{r}
library(taxald)

create_taxadb()
```

@@

@@

```{r}
df <- descendents(name = "Aves", rank = "class", authority="col")
```

>>>>

```{r}
library(taxald)
```

```{r eval=FALSE}
create_taxadb()
```

@@

```{r}
library(tictoc) # let's display timing of queries for reference
```

@@

```{r}
tic()
df <- descendents(name = "Aves", rank = "class", authority="col")
toc()
```

How many species did we get?

```{r}
length(df$name)
```

In general, this species list could have come from anywhere (i.e. some particular research project) and not from a single authority.

We can get the full hierachical classification for this list of species:

```{r}
tic()
hierarchy(df$name)
toc()
```
